### 2021-04-08 ch04_papers_ecs_tcr_assessment/papers_ecs_tcr_assessment.tex
Spell- and grammer-checked chapter 2

Another possible reason for the high climate sensitivity in the \acs{CMIP}6
ensemble is related to cloud feedbacks \autocite{Bock2020}. As already
discussed in \cref{subsec:02:climate_feedbacks}, uncertainties in cloud
feedbacks are a major source of uncertainty of \ac{ECS} in modern \acp{ESM}
\autocite{Boucher2013, Flato2013}. Thus, changes in processes that are related
to cloud feedbacks immediately impact the climate models' climate sensitivity.
The particular feedback mechanism that is thought to be relevant for the high
\ac{ECS} in \acs{CMIP}6 is connected to cloud phase changes over the Southern
Ocean that are present in earlier \ac{CMIP} generations (\eg{} \acs{CMIP}5).
This so-called \emph{cloud phase change feedback} is illustrated in
\cref{fig:04:cloud_phase_change_feedback} (green arrows). As the climate warms,
the predominantly ice clouds over the Southern Ocean in these climate models
become liquid clouds \autocite{McCoy2015}. As a result, the cloud will get more
reflective to the incoming solar radiation since a cloud consisting of smaller
liquid droplets reflects more sunlight than a cloud consisting of larger ice
crystals (for a fixed water content), which has a cooling effect on the climate
system. In addition, predominantly liquid clouds tend to precipitate less than
mixed-phase clouds (composed of liquid water and ice). This leads to a higher
liquid water content of the cloud and a further amplification of the cooling
effect. Overall, this forms a strong negative shortwave cloud feedback over the
Southern Ocean in climate models from previous \ac{CMIP} generations.

>>>>

Another possible reason for the high climate sensitivity in the \acs{CMIP}6
ensemble is related to cloud feedbacks \autocite{Bock2020}. As already
discussed in \cref{subsec:02:climate_feedbacks}, uncertainties in cloud
feedbacks are a major source of uncertainty of \ac{ECS} in modern \acp{ESM}
\autocite{Boucher2013, Flato2013}. Thus, changes in processes that are related
to cloud feedbacks immediately impact the climate models' climate
sensitivities. The particular feedback mechanism that is thought to be relevant
for the high \ac{ECS} in \acs{CMIP}6 is connected to cloud phase changes over
the Southern Ocean that are present in earlier \ac{CMIP} generations (\eg{}
\acs{CMIP}5). This so-called \emph{cloud phase change feedback} is illustrated
in \cref{fig:04:cloud_phase_change_feedback} (green arrows). As the climate
warms, the predominantly ice clouds over the Southern Ocean in these climate
models become liquid clouds \autocite{McCoy2015}. As a result, the cloud will
get more reflective to the incoming solar radiation since a cloud consisting of
smaller liquid droplets reflects more sunlight than a cloud consisting of
larger ice crystals (for a fixed water content), which has a cooling effect on
the climate system. In addition, predominantly liquid clouds tend to
precipitate less than mixed-phase clouds (composed of liquid water and ice).
This leads to a higher liquid water content of the cloud and a further
amplification of the cooling effect. Overall, this forms a strong negative
shortwave cloud feedback over the Southern Ocean in climate models from
previous \ac{CMIP} generations.
